Performance of two different ontological and data access methods

### 2014-07-03 cold2014/magnus.tex
reference spec for GR
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@730 43ef1190-90fd-4dd7-a769-d0121f02b80e

The Volkswagen solution builds upon GoodRelations, which is a web
vocabulary for e-commerce and was launched in 2008 and is now
widespread. GoodRelations.~\cite{GR} GoodRelations can be used for
detailed information about products to be sold online.

@@

\subsection{Planning the experiment}
Like other approaches, there are several steps in doing experiments with
DoE.  First one has to state an objective which is important to give
the experiment a purpose.  The next step is to choose a response. The
response is the experimental outcome or observation. There may be
multiple responses in an experiment. In this experiment there will be
one response and that is the response time on a HTTP post against the
application.  These first two steps are the same for all the
experiments in this thesis.

@@

The fourth step in planning is to choose the experimental plan. Here
we will use one specific approach. The approach is called \emph{full
  factorial experiment} which we will go into more detail about in the
next sub-section. There are other approaches like fractional factorial
experiment, but they were not applicable or relevant to this thesis.
The last three steps of planning the experiment are performing the
experiment, analyzing the output and in the end drawing
conclusions. More about these steps will be taken individually at each
experiment.~\cite{PlanExp}

@@

To evaluate the graphs we have used a method in the \textsf{FrF2} R
package called \textsf{DanielPlot}. This method assumes that the
estimated effects are normally distributed with means equal to the
effects. The means of all estimated effects are zero. Resulting in a
plot where the estimated effect would end up on a straight line. This
plot is then testing whether all the estimated effects have the same
distribution. All deviations of the straight line indicates a
significant factor. In our results we have used the absolute value of
the effects, also called a half-normal plot. The advantages of using
the half-normal plot is that all large estimated effects will end up
in the top right corner. This means that the highest performance
significance will end up in
the top right corner.~\cite{Plotting} \\
Here is a quick explanation of the axes shown in each graph.  The X
axis will show the absolute effect of each factor, shown in time. The
values on the X axis is represented in seconds which means that the a
plot will have a significance measured in seconds.  The Y axis shows
the half-normal scores. There are two way of representing the graph
and that is with either half-normal plots or normal plots. With
half-normal the effects on the X axis are shown with the absolute
effect. This means that all factors are placed with a positive
half-normal score. This is to avoid visual misleading scores because
with the normal scores, deviations from the line on negative scores
might confuse the reader who are evaluating the charts.  The scores
them selves are a measure for which factor that is the most
significant.  We have also set  the significance level at $\alpha =
0.05$, where \textsf{DanielPlot} is using Lenth's method for the
analysis of unreplicated factorials. % TODO: Need a citation here.

@@

>>>>

The Volkswagen solution builds upon GoodRelations\cite{GRQual}, which
is a web vocabulary for e-commerce and was launched in 2008 and is now
widespread.  GoodRelations can be used for detailed information about
products to be sold online.

@@

\subsection{Planning the experiment}
Like other approaches, there are several steps in doing experiments
with DoE. A good textbook on the subject is \cite{PlanExp}. First one
has to state an objective which is important to give the experiment a
purpose.  The next step is to choose a response. The response is the
experimental outcome or observation. There may be multiple responses
in an experiment. In this experiment there will be one response and
that is the response time on a HTTP post against the application.
These first two steps are the same for all the experiments in this
thesis.

@@

The fourth step in planning is to choose the experimental plan. Here
we will use one specific approach. The approach is called \emph{full
  factorial experiment} which we will go into more detail about in the
next sub-section. There are other approaches like fractional factorial
experiment, but they were not applicable or relevant to this thesis.
The last three steps of planning the experiment are performing the
experiment, analyzing the output and in the end drawing
conclusions. More about these steps will be taken individually at each
experiment.

@@

To evaluate the graphs we have used a method in the \textsf{FrF2} R
package called \textsf{DanielPlot}. This method assumes that the
estimated effects are normally distributed with means equal to the
effects. The means of all estimated effects are zero. Resulting in a
plot where the estimated effect would end up on a straight line. This
plot is then testing whether all the estimated effects have the same
distribution. All deviations of the straight line indicates a
significant factor. In our results we have used the absolute value of
the effects, also called a half-normal plot. The advantages of using
the half-normal plot is that all large estimated effects will end up
in the top right corner. This means that the highest performance
significance will end up in the top right corner. The
axes themselves are not important to understand the plot nor the
results, refer to \cite{PlanExp} for details.
We have also set  the significance level at $\alpha =
0.05$, where \textsf{DanielPlot} is using Lenth's method for the
analysis of unreplicated factorials.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{bibliography}
